Paper_Figure

### 2025-04-29 README.Rmd
update readme

>>>>

## Docker Installation

Alternatively, we provide a Docker environment with LMD and all its dependencies pre-installed. The pre-built Docker image can be downloaded using:

``` bash
docker pull ruiqi0130/lmd-rstudio:lastest
```

and to run the docker container:

``` bash
docker run -it --rm --name lmd -p 8029:8787  -v /data/:/data/   docker.io/ruiqi0130/lmd-rstudio:latest
```

Here, change `/data:/data` to `<your_local_data_directory>:/data`. A rstudio will be on port 8029.
